Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
typo

We now focus on the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$.
Since~$\Asso[n]$ leaves in a hyperplane of~$\R^{n+1}$, so does its normal fan.
Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = 0}$ and~$\pi : \R^{n+1} \to \HH$ denote the orthogonal projection.
The following fans are illustrated in \cref{fig:lodayFans} in dimension~$2$ and~$3$.

@@

\begin{example}
\label{exm:typeConeAsso}
Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$.
It has $3$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).

>>>>

We now focus on the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$.
Since~$\Asso[n]$ lives in a hyperplane of~$\R^{n+1}$, so does its normal fan.
Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = 0}$ and~$\pi : \R^{n+1} \to \HH$ denote the orthogonal projection.
The following fans are illustrated in \cref{fig:lodayFans} in dimension~$2$ and~$3$.

@@

\begin{example}
\label{exm:typeConeAsso}
Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$ (this is the type cone studied in \cref{ex:typecone}).
It has $3$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).
